Data irregularities across six implicit learning articles: Comments on Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)

### 2022-02-04 docs/manuscript/manuscript.Rmd
update: fix wording

Cohen's *d* is used to describe the standardized mean difference of an effect and values can range between 0 and infinity in both the negative and positive direction. We calculated absolute values so that all effects were positive. Cohen's $d_{s}$ [@cohen1988] is the observed difference between group means divided by their pooled standard deviation [see @lakens2013 for a detailed discussion]. Conventional benchmarks for small, medium, and large effects are *d* = .2, .5, and .8, respectively [@cohen1962]; however, this *cargo-cult* approach to effect size interpretation has been heavily discouraged [see @correll2020; @field2016; @lakens2013; @thompson2007 for discussions]. Recently, an analysis of 6447 Cohen's *d* statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's *d* values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021]. In the field of motor learning, recent meta-analyses have found average effect sizes in the published literature of *d* = .19 [@mckay2021b], *d* = .54 [@mckay2021a], and *d* = .71 [@lohse2016].

>>>>

Cohen's *d* is used to describe the standardized mean difference of an effect and values can range between 0 and infinity in both the negative and positive direction. We calculated absolute values so that all effects were positive. Cohen's $d_{s}$ [@cohen1988] is the observed difference between group means divided by their pooled standard deviation [see @lakens2013 for a detailed discussion]. Conventional benchmarks for small, medium, and large effects are *d* = .2, .5, and .8, respectively [@cohen1962]; however, this *mindless* approach to effect size interpretation has been heavily discouraged [see @correll2020; @field2016; @lakens2013; @thompson2007 for discussions]. Recently, an analysis of 6447 Cohen's *d* statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's *d* values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects [@lovakov2021]. In the field of motor learning, recent meta-analyses have found average effect sizes in the published literature of *d* = .19 [@mckay2021b], *d* = .54 [@mckay2021a], and *d* = .71 [@lohse2016].
